Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-16 paper/method.tex
Space squeezing.
Space saving.

\paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process by using a $75\times75$ pixel patch at the center of an existing boundary. This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset\footnote{\scriptsize{\url{http://openconnectomeproject.org/}}}. If the boundary length is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and average the resulting scores weighted by the boundary length coverage per patch.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
\end{center}
%  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{Our guided proofreading user interface. A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Hovering highlights the current selection with a blue border, and a mouse click confirms the choice and advances to the next potential error.}
\label{fig:ui}
\end{figure}

>>>>

\paragraph{Classifier Inputs.} To train the CNN, we consider boundary context in the decision making process via a $75\times75$ patch over the center of an existing boundary. This size covers approximately $80\%$ of all boundaries in the 6~nm Mouse S1 AC3 Open Connectome Project dataset. If the boundary is not fully covered, we sample up to 10 non-overlapping patches along the boundary, and average the resulting scores weighted by the boundary length coverage per patch.
%\footnote{\scriptsize{\url{http://openconnectomeproject.org/}}}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v4.pdf}
\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{User interface. A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Confirming the choice advances to the next potential error.} % Hovering highlights the current selection with a blue border, and a}
\label{fig:ui}
\end{figure}
